Thermoeconomic Analysis of Biodiesel Production from Used Cooking Oils

### 2015-05-24 paper.tex
Correct some table formats
Correct some table formats from published version, and reformatting the
figure 1.
Final Version

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Figure1}
\caption[Flow diagram of a biodiesel plant producing with Used Cooking Oil]{Flow diagram of a biodiesel plant producing with used cooking oil. Source: CIEMAT \cite{CIEMAT2005}. } 
\label{fig1}
\end{figure}

@@

\begin{table}[H]
 \centering \small
 \caption{Fuel-product table.}
	 \vskip 2pt
 \begin{tabulary}{\textwidth}{lccCCCCCCc}
 \toprule
   &  & \multirow{2}[6]{1.5cm}{\centering \textbf{Final Product}} & \multicolumn{5}{c}{\textbf{Process Resources}} & \\
 \cmidrule(r){4-8}
   &  & & \textbf{1} & \boldmath$\cdots$ & \textbf{j } & \boldmath$\cdots$ & \textbf{n} & \textbf{Total} \\
		\midrule
External &  &  & \multirow{2}[1]{*}{$E_{01}$} & \multirow{2}[1]{*}{$\cdots$} & \multirow{2}[1]{*}{$E_{0j}$} & \multirow{2}[1]{*}{$\cdots$} & \multirow{2}[1]{*}{$E_{0n}$} & \multirow{2}[1]{*}{$P_0$} \\
 Resources &  &  &  &  &  &  &  & \\
 \multirow{5}[0]{2cm}{Process Products} & 1 & $E_{10}$ & $E_{11}$ & $\cdots$ & $E_{1j}$ &$\cdots$ & $E_{1n}$ & $P_1$ \\
   & $\vdots$ & $\vdots$ & $\vdots$ & & $\vdots$ & & $\vdots$ & $\vdots$ \\
   & i & $E_{i0}$ & $E_{i1}$ & $\cdots$ & $E_{ij}$ & $\cdots$ & $E_{in}$ & $P_i$ \\
   & $\vdots$ & $\vdots$ & $\vdots$ & & $\vdots$ & & $\vdots$ & $\vdots$\\
   & n & $E_{n0}$ & $E_{n1}$ & $\cdots$ & $E_{nj}$ & $\cdots$ & $E_{nn}$ & $P_n$ \\
	 \midrule
 Total &  & $F_0$ & $F_1$ & $\cdots$ & $F_j$ & $\cdots$ & $F_n$ & \\
 \bottomrule
 \end{tabulary}%
 \label{table2}%
\end{table}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[H]
 \centering \footnotesize
 \caption{Exergy and cost of flows of the UCO biodiesel pathway.}
 \begin{tabular}{ccccccccc}
 \toprule
   &  & & &  & \multicolumn{2}{c}{\bf Exergy} & \multicolumn{2}{c}{\bf Cost} \\
 \cmidrule(r){6-7} \cmidrule(r){8-9}
 {\bf Material} & {\bf Process} & {\bf I/O} & {\bf Unit} \textbf{(u)} & \textbf{u/\kfame} & \textbf{MJ/u} & \textbf{MJ/\kfame} & \textbf{MJ/u} & \textbf{MJ/\kfame} \\
 \midrule
 Diesel   & 1 & Input & MJ & 0.6459 & 1.0000 & 0.6459 & 1.1773 & 0.7604 \\
 UCO   & 1 & Output & kg & 1.3368 & 39.5994 & 52.9364 & -  & - \\
 Diesel   & 2 & Input & MJ & 0.0371 & 1.0000 & 0.0371 & 1.1773 & 0.0437 \\
 Electricity & 2 & Input & MJ & 0.4679 & 1.0000 & 0.4679 & 2.8690 & 1.3423 \\
 UCO recycled & 2 & Output & kg & 1.0300 & 39.5994 & 40.7873 & -  & - \\
 Methanol  & 3 & Input & kg & 0.1550 & 23.1540 & 3.5889 & 30.3074 & 4.6977 \\
 KOH   & 3 & Input & kg & 0.0277 & 0.8229 & 0.0228 & 13.3852 & 0.3708 \\
 \ce{H2SO4} & 3 & Input & kg & 0.0170 & 1.6417 & 0.0279 & 2.6295 & 0.0447 \\
 Diesel   & 3 & Input & MJ & 1.5651 & 1.0000 & 1.5651 & 1.1773 & 1.8426 \\
 Electricity & 3 & Input & MJ & 0.4713 & 1.0000 & 0.4713 & 2.8690 & 1.3522 \\
 Crude FAME & 3 & Output & kg & 1.0100 & 39.8548 & 40.2533 & -  & - \\
 Crude Glycerol & 3 & Output & kg & 0.2000 & 23.6779 & 4.7356 & -  & - \\
 HCl   & 4 & Input & kg & 0.0406 & 1.3409 & 0.0544 & 5.2484 & 0.2131 \\
 Diesel   & 4 & Input & MJ & 0.0749 & 1  & 0.0749 & 1.1773 & 0.0882 \\
 Electricity & 4 & Input & MJ & 0.0187 & 1.0000 & 0.0187 & 2.869 & 0.0535 \\
 FAME   & 4 & Output & kg & 1  & 39.8376 & 39.8376 & -  & - \\
 \bottomrule
 \end{tabular}%
 \label{table3}%%please reference in the text before presenting
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[H]
\centering 
\footnotesize
\caption[F--P Tables UCO biodiesel]{F-P (fuel-product) tables for UCO biodiesel (MJ/kg FAME).}
\begin{tabularx}{0.9\textwidth}{ZZZZZZZ}
\toprule
 & \boldmath$F_0$ & \boldmath$F_1$ & \boldmath$F_2$ & \boldmath$F_3$ &\boldmath $F_4$ & \textbf{Total} \\
\midrule
% Table generated by Excel2LaTeX from sheet 'Cost UCO'
$P_0$ &  & 53.58 & 0.51 & 5.68 & 0.15 & 59.91 \\

$P_1$ & 0.00 & 0.00 & 52.94 & 0.00 & 0.00 & 52.94 \\
$P_2$ & 0.00 & 0.00 & 0.00 & 40.79 & 0.00 & 40.79 \\
$P_3$ & 4.74 & 0.00 & 0.00 & 0.00 & 40.25 & 44.99 \\
$P_4$ & 39.84 & 0.00 & 0.00 & 0.00 & 0.00 & 39.84 \\
\midrule
Total & 44.58 & 53.58 & 53.44 & 46.46 & 40.40 & \\
\bottomrule
\end{tabularx}%
\label{table4}%
\end{table}%

@@

\begin{table}[H]
 \centering
 \caption[Cost analysis for UCO biodisel]{Cost analysis for UCO biodiesel (MJ/kg FAME).}
 \begin{tabularx}{0.8\textwidth}{ccZZZZZ}
 \toprule
  &       & \boldmath$\ems[nrs]{C}{e}$ & \boldmath$C_P$ & \boldmath$\ems[rs]{C}{P}$ & \boldmath$\ems[nrs]{C}{P}$ & \boldmath$\rho$ \\
 \textbf{No. } &\textbf{ Process     }& \textbf{MJ/Kg } & \textbf{MJ/kg} & \textbf{MJ/Kg} & \textbf{MJ/kg} & \textbf{\%} \\
 \midrule
 1 & Collection   & 0.76 & 53.697 & 52.936 & 0.760 & 98.58 \\
 2 & Refining    & 1.39 & 55.083 & 52.936 & 2.146 & 96.10 \\
 3 & Esterification  & 8.31 & 63.391 & 52.936 & 10.454 & 83.51 \\
 4 & FAME after treatment & 0.35 & 57.073 & 47.364 & 9.709 & 82.99 \\
 \bottomrule
 \end{tabularx}%
 \label{table5}%
\end{table}%

@@

\begin{table}[H]
 \centering
 \small
 \caption{Relative impact of external resources on the production cost of FAME from UCO.}
 \begin{tabular}{ccccc}
 \toprule
 \textbf{Flow} & \textbf{Collection} &\textbf{ Recycling} & \textbf{Esterification} & \textbf{FAME} \\
 \midrule
 Diesel & 1.0000 & 0.3746 & 0.2532 & 0.2530 \\
 Methanol & 0.0000 & 0.0000 & 0.4433 & 0.4273 \\
 Electricity & 0.0000 & 0.6254 & 0.2594 & 0.2554 \\
 KOH & 0.0000 & 0.0000 & 0.0350 & 0.0337 \\
 \ce{H2SO4} & 0.0000 & 0.0000 & 0.0042 & 0.0041 \\
 HCl & 0.0000 & 0.0000 & 0.0000 & 0.0217 \\
 \bottomrule
 \end{tabular}%
 \label{table6}%
\end{table}%

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.55\textwidth]{Figure1}
\caption[Flow diagram of a biodiesel plant producing with Used Cooking Oil]{Flow diagram of a biodiesel plant producing with used cooking oil. Source: CIEMAT \cite{CIEMAT2005}. } 
\label{fig1}
\end{figure}

@@

\begin{table}[H]
 \centering \small
 \caption{Fuel-product table.}
	 \vskip 2pt
 \begin{tabulary}{\textwidth}{lccCCCCCCc}
 \toprule
   &  & \multirow{2}[6]{1.5cm}{\centering \textbf{Final Product}} & \multicolumn{5}{c}{\textbf{Process Resources}} & \\
 \cmidrule(r){4-8}
   &  & & \textbf{1} & \boldmath$\cdots$ & \textbf{j } & \boldmath$\cdots$ & \textbf{n} & \textbf{Total} \\
		\midrule
\bf External &  &  & \multirow{2}[1]{*}{$E_{01}$} & \multirow{2}[1]{*}{$\cdots$} & \multirow{2}[1]{*}{$E_{0j}$} & \multirow{2}[1]{*}{$\cdots$} & \multirow{2}[1]{*}{$E_{0n}$} & \multirow{2}[1]{*}{$P_0$} \\
 \bf Resources &  &  &  &  &  &  &  & \\
 \multirow{5}[0]{2cm}{\bf Process Products} & 1 & $E_{10}$ & $E_{11}$ & $\cdots$ & $E_{1j}$ &$\cdots$ & $E_{1n}$ & $P_1$ \\
   & $\vdots$ & $\vdots$ & $\vdots$ & & $\vdots$ & & $\vdots$ & $\vdots$ \\
   & i & $E_{i0}$ & $E_{i1}$ & $\cdots$ & $E_{ij}$ & $\cdots$ & $E_{in}$ & $P_i$ \\
   & $\vdots$ & $\vdots$ & $\vdots$ & & $\vdots$ & & $\vdots$ & $\vdots$\\
   & n & $E_{n0}$ & $E_{n1}$ & $\cdots$ & $E_{nj}$ & $\cdots$ & $E_{nn}$ & $P_n$ \\
	 \midrule
 \textbf{Total} &  & $F_0$ & $F_1$ & $\cdots$ & $F_j$ & $\cdots$ & $F_n$ & \\
 \bottomrule
 \end{tabulary}%
 \label{table2}%
\end{table}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[H]
 \centering \footnotesize
 \caption{Exergy and cost of flows of the UCO biodiesel pathway.}
 \begin{tabular}{lcccccccc}
 \toprule
   &  & & &  & \multicolumn{2}{c}{\bf Exergy} & \multicolumn{2}{c}{\bf Cost} \\
 \cmidrule(r){6-7} \cmidrule(r){8-9}
 {\bf Material} & {\bf Process} & {\bf I/O} & {\bf Unit}(u) & { u/\kfame} & MJ/u & MJ/\kfame & MJ/u & MJ/\kfame \\
 \midrule
 Diesel   & 1 & Input & MJ & 0.6459 & 1.0000 & 0.6459 & 1.1773 & 0.7604 \\
 UCO   & 1 & Output & kg & 1.3368 & 39.5994 & 52.9364 & -  & - \\
 Diesel   & 2 & Input & MJ & 0.0371 & 1.0000 & 0.0371 & 1.1773 & 0.0437 \\
 Electricity & 2 & Input & MJ & 0.4679 & 1.0000 & 0.4679 & 2.8690 & 1.3423 \\
 UCO recycled & 2 & Output & kg & 1.0300 & 39.5994 & 40.7873 & -  & - \\
 Methanol  & 3 & Input & kg & 0.1550 & 23.1540 & 3.5889 & 30.3074 & 4.6977 \\
 KOH   & 3 & Input & kg & 0.0277 & 0.8229 & 0.0228 & 13.3852 & 0.3708 \\
 \ce{H2SO4} & 3 & Input & kg & 0.0170 & 1.6417 & 0.0279 & 2.6295 & 0.0447 \\
 Diesel   & 3 & Input & MJ & 1.5651 & 1.0000 & 1.5651 & 1.1773 & 1.8426 \\
 Electricity & 3 & Input & MJ & 0.4713 & 1.0000 & 0.4713 & 2.8690 & 1.3522 \\
 Crude FAME & 3 & Output & kg & 1.0100 & 39.8548 & 40.2533 & -  & - \\
 Crude Glycerol & 3 & Output & kg & 0.2000 & 23.6779 & 4.7356 & -  & - \\
 HCl   & 4 & Input & kg & 0.0406 & 1.3409 & 0.0544 & 5.2484 & 0.2131 \\
 Diesel   & 4 & Input & MJ & 0.0749 & 1  & 0.0749 & 1.1773 & 0.0882 \\
 Electricity & 4 & Input & MJ & 0.0187 & 1.0000 & 0.0187 & 2.869 & 0.0535 \\
 FAME   & 4 & Output & kg & 1  & 39.8376 & 39.8376 & -  & - \\
 \bottomrule
 \end{tabular}%
 \label{table3}%%please reference in the text before presenting
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[H]
\centering 
\footnotesize
\caption[F--P Tables UCO biodiesel]{F-P (fuel-product) tables for UCO biodiesel (MJ/kg FAME).}
\begin{tabularx}{0.9\textwidth}{ZZZZZZZ}
\toprule
 & $F_0$ & $F_1$ &$F_2$ &$F_3$ &$F_4$ & \textbf{Total} \\
\midrule
% Table generated by Excel2LaTeX from sheet 'Cost UCO'
$P_0$ &  & 53.58 & 0.51 & 5.68 & 0.15 & 59.91 \\
$P_1$ & 0.00 & 0.00 & 52.94 & 0.00 & 0.00 & 52.94 \\
$P_2$ & 0.00 & 0.00 & 0.00 & 40.79 & 0.00 & 40.79 \\
$P_3$ & 4.74 & 0.00 & 0.00 & 0.00 & 40.25 & 44.99 \\
$P_4$ & 39.84 & 0.00 & 0.00 & 0.00 & 0.00 & 39.84 \\
\midrule
\bf Total & 44.58 & 53.58 & 53.44 & 46.46 & 40.40 & \\
\bottomrule
\end{tabularx}%
\label{table4}%
\end{table}%

@@

\begin{table}[H]
 \centering
 \caption[Cost analysis for UCO biodisel]{Cost analysis for UCO biodiesel (MJ/kg FAME).}
 \begin{tabularx}{0.8\textwidth}{clZZZZZ}
 \toprule
  &       & \boldmath$\ems[nrs]{C}{e}$ & \boldmath$C_P$ & \boldmath$\ems[rs]{C}{P}$ & \boldmath$\ems[nrs]{C}{P}$ & \boldmath$\rho$ \\
 \textbf{No}.  & \textbf{Process} & MJ/Kg & MJ/kg & MJ/Kg & MJ/kg & \% \\
 \midrule
 1 & Collection   & 0.76 & 53.697 & 52.936 & 0.760 & 98.58 \\
 2 & Refining    & 1.39 & 55.083 & 52.936 & 2.146 & 96.10 \\
 3 & Esterification  & 8.31 & 63.391 & 52.936 & 10.454 & 83.51 \\
 4 & FAME after treatment & 0.35 & 57.073 & 47.364 & 9.709 & 82.99 \\
 \bottomrule
 \end{tabularx}%
 \label{table5}%
\end{table}%

@@

\begin{table}[H]
 \centering
 \small
 \caption{Relative impact of external resources on the production cost of FAME from UCO.}
 \begin{tabular}{lcccc}
 \toprule
 \textbf{Flow} & \textbf{Collection} &\textbf{ Recycling} & \textbf{Esterification} & \textbf{FAME} \\
 \midrule
 Diesel & 1.0000 & 0.3746 & 0.2532 & 0.2530 \\
 Methanol & 0.0000 & 0.0000 & 0.4433 & 0.4273 \\
 Electricity & 0.0000 & 0.6254 & 0.2594 & 0.2554 \\
 KOH & 0.0000 & 0.0000 & 0.0350 & 0.0337 \\
 \ce{H2SO4} & 0.0000 & 0.0000 & 0.0042 & 0.0041 \\
 HCl & 0.0000 & 0.0000 & 0.0000 & 0.0217 \\
 \bottomrule
 \end{tabular}%
 \label{table6}%
\end{table}%
